---
title: "naptime: A Robust Flexible Sys.sleep Replacement"
author: "Timothy Gann & Russell S. Pierce"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{naptime: A Robust Flexible Sys.sleep Replacement}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# naptime

```{r, echo=FALSE, results='hide'}
library(naptime)
```

The premise of naptime is two fold.  

1. Delays in R code should never result in an error.
2. Functions should accept multiple inputs types, but result in a single output type.  

In response to these considerations `naptime::naptime()` either sleeps for the specified duration, or passes forward with a warning.  It has the same argument name as `base::Sys.sleep()` and a nearly identical behavior in response to numeric inputs.  As such, it can be nearly used as a drop-in replacement for `base::Sys.sleep()`.  

The one notable exception to identical behavior is the input value of `Inf`.  `base::Sys.sleep()` will sleep indefiniately in reponse to `Inf`.  In contrast, `naptime::naptime()` will sleep the default duration.

# Options
All options are set via base::options().

* `naptime.default_delay`.  If left unchanged, the default delay is `.1` seconds.
* `naptime.warnings`.  **This feature not yet available**.  If left unchanged, the default is `TRUE, to show warnings.

# Polymorphic inputs
naptime() accepts a wide variety of inputs.  If you find a reasonable input-type for which `naptime::naptime()` doesn't have a reasonable response, please file (an issue)[https://github.com/drknexus/naptime/issues].

* `numeric` Time in seconds

```{r}
naptime(1)
```

* `Period` Any positive time difference regardless of units
* `character` A time in the format of yyyy-mm-dd hh:mm:ss UTC.

In addition, naptime will handle some specific errors:
* All negative intervals will be converted to a delay of 0
* All non-finite intervals will be converted to a default delay
* All inputs that produce an error will be converted to a default delay

# Author's Note
The initial draft of this code was written by Timothy Gann under a spec drafted by Russell Pierce.  Subsequent modifications to the code, packaging, and tests were written by Russell Pierce.  Russell Pierce is the current maintainer and responsible party for this package.
